### 2012-10-28 intention motor representation joint action (paper 3)/conf budapest philosophy 2012-11/shared agency and motor representation.tex
working on it

@@

\section{Introduction}
Shared agency is paradigmatically involved when two (or more) people 
	paint a house together \citep{Bratman:1992mi}, 
	lift a heavy sofa together \citep{Velleman:1997oo}, 
	prepare a hollandaise sauce together \citep{Searle:1990em}, 
	go to Chicago together \citep{Kutz:2000si}, 
	and walk together \citep{gilbert_walking_1990}.
In developmental psychology paradigm cases involving shared agency include  two people 
	tidying up the toys together \citep{Behne:2005qh},
	cooperatively pulling handles in sequence to make a dog-puppet sing \citep{Brownell:2006gu},
	bouncing a ball on a large trampoline together \citep{Tomasello:2007gl}.

Which representations %and processes 
are needed in giving a philosophical account of shared agency?
Philosophers have so far considered intentions and other propositional attitudes but ignored the possibility that appeal to motor representation may also be needed. 
%To considerations jointly motivate considering whether fully characterising shared agency may require appeal to motor representation.
By contrast, concerning individual rather than shared agency, some have argued that motor representation may play a role in explaining agency \citep[e.g.][]{pacherie:2000_content,pacherie:2008_action,butterfill:2012_intention}. 
Scientific research provides evidence that motor representations sometimes play a role in enabling agents to exercise shared agency, as we shall explain in detail below.
So it is possible to ask whether appeal to motor representation  %might not only sometimes enable agents to exercise shared agency but also
could also play a role in explaining what shared agency is.
In this paper we argue that it could.
Shared agency is not only a matter of what we intend or know, or of our commitments: in some cases it also constitutively involves certain structures of motor representation, or so we aim to show.

%A \emph{joint action} is an action or event involving shared agency.

Before starting on the argument, let us step back to ask why anyone might want a philosophical account of shared agency.
Shared agency raises a tangle of scientific and philosophical questions.  Psychologically we want to know which mechanisms make it possible \citep{vesper_minimal_2010}.  
Developmentally we want to know when shared agency emerges, what it presupposes and whether it might somehow facilitate socio-cognitive, pragmatic or symbolic development \citep{Moll:2007gu,Hughes:2004zj,Brownell:2006gu}.  
Phenomenologically we want to characterise what (if anything) is special about experiences of action and agency when shared agency is involved \citep{Pacherie:2010fk}.  
Metaphysically we want to know what kinds of entities and structures are implied by the existence of shared agency \citep{Gilbert:1992rs,Searle:1994lb}.  
And normatively we want to know what kinds of commitments (if any) are entailed by shared agency and how these commitments arise \citep{Roth:2004ki}.
%, plus a formal account of how practical reasoning for joint action differs (if at all) from individual practical reasoning \citep{Sugden:2000mw,Gold:2007zd}
One use for a philosophical account of shared agency is to support investigation of these questions by providing a principled way to distinguish shared from individual agency (as \citealp{Bratman:2009lv} suggests).  
Or, if there is more than one form of shared agency, the account should provide a principled way of distinguishing among forms of individual and shared agency.   
%
%To make this aim vivid, consider some well-known contrast cases.
%Contrast cases are pairs of episodes which are similar in terms of the behaviour and coordination they involve but where one episode exemplifies shared agency  while the other does not.  
%Thus \citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
%The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together involves shared agency whereas merely walking side by side does not. 
%Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first  case involves shared agency, the second does not; but the same movements occur in both.%
%\footnote{
%Compare \citet{Pears:1971fk} who uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents.
%}  
%
%Contrast cases invite the question, 
%How do actions involving shared agency differ from merely parallel actions involving  only individual agency? 
%Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
%And Searle’s example shows that the difference between shared agency and parallel individual agency can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too. 
%Minimally, a philosophical account of shared agency should identify a difference in these and other contrast cases.
%

As already mentioned, our aim is to show that distinguishing individual from shared agency sometimes involves appeal to certain structures of motor representation.
First we outline a standard approach to shared agency.

\section{Shared intention}
On the leading, best developed accounts of shared agency in philosophy and psychology, 
shared agency is explained  in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared intention.
For two or more agents to exercise shared agency is for them to have a shared intention and for this shared intention to be appropriately related to their actions.
Such actions are called a `shared intentional activity' (\citealp[p.\ 142]{Bratman:1999fr}).%
%On this widely held view, the difference between our walking together and two strangers merely walking side-by-side is that one event is appropriately related to a shared intention whereas the other is not.

Explaining shared agency in terms of shared intention pushes us back to the question, What is shared intention?
The term `shared intention' is potentially misleading.
On many accounts, shared intentions are neither shared nor intentions.
And there is much divergence on what shared intention is.
Some hold that it differs from
ordinary intention with respect to the attitude involved (\citealp{Searle:1990em}). 
Others have explored the notion that it differs from ordinary intention with respect to its subject, which is plural \citep{Gilbert:1992rs,helm_plural_2008}, 
or that it differs from ordinary intention in the way it arises, namely through team reasoning \citep{Gold:2007zd}, 
or that it involves distinctive obligations or commitments to others (\citealp{Gilbert:1992rs}; \citealp{Roth:2004ki}).
Opposing all such views, \citet{Bratman:1992mi,Bratman:2009lv} argues that shared intention can be realised by multiple ordinary individual intentions and other attitudes whose contents interlock in a distinctive way.

To avoid the need to take sides on what precisely shared intention is, 
let us abstract from some details. 
There are features of shared intention on which there should be widespread agreement.
Minimally, a shared intention stands to the actions comprising a shared intentional activity in roughly the way that an ordinary, individual intention stands to an ordinary, individual action.
Now an ordinary, individual intention represents an outcome, coordinates an agent's actions, and coordinates the agent's actions in such a way that, normally, this coordination would facilitate the occurrence of the represented outcome.
Similarly, 
on almost any account,
a shared intention involves there being a single outcome which each agent represents, where these representations coordinate the several agents' actions and coordinate them in such a way that, normally, the coordination would facilitate the occurrence of the represented outcome.

Our view involves rejecting the claim that a full account of shared agency can be given in terms of shared intention alone.
Instead, we shall argue, it is also necessary to appeal to certain structures of motor representation. 
Note, however, that our view is compatible with various weaker claims linking shared intention to shared agency.
In particular, our view is consistent with the claims that appeal shared intention is also needed in giving an account of shared agency, 
and that \emph{some forms} of shared agency can be fully characterised by appeal to shared intention alone.
Our view is also consistent with the claim that all exercises of shared agency involve shared intentions in some way.%
\footnote{
See \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  
Related claims are made by 
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si},  
	\citet[p.\ 117]{rakoczy_pretend_2006},  and
	\citet{Tollefsen:2005vh}.
}

Why might anyone hold, contrary to what we shall argue, that a full account of shared intention without appeal to ingredients other than shared intention? 
Two considerations might initially appear favour this view.

First, if someone thought that it is possible to distinguish systematically between the contrast cases by appeal to shared intention (and perhaps only by appeal to shared intention), this could motivate holding that for an event to be a joint action is for it to be appropriately related to a shared intention.
We shall argue, however, that distinguishing systematically between the contrast cases cannot be done entirely in terms of shared intention. 
[*CV: this argument is missing from this draft.]

{\label{text:second_consideration} A second, related consideration} which might appear to favour this view is a parallel between shared agency and ordinary, individual agency.
If a full account of individual agency could be given by appeal to intention and other propositional attitudes with no appeal to motor representation,
then it would seem unlikely that giving a full account of shared agency must somehow involve appeal to motor representation.
However, as mentioned above, some have argued that fully characterising individual agency will require appeal to motor representation as well as intention \citep{pacherie:2000_content,butterfill:2012_intention}. 
Given these arguments, the parallel between individual and shared agency motivates considering the possibility that  there is a constitutive role for motor representation in shared agency. 
We also note that some philosophers allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' (\citeyear[p.\ 251]{bratman:2000_valuing}; see \citealp[pp.\ 137--8]{Bratman:1987xw} for further justification). 
Certainly, then, it is not unreasonable to question the claim that a full account of ordinary, individual agency can be given just in terms of intention.

\section{Motor representation}
Since we aim to argue that a fully adequate account of shared agency must appeal to motor representation, it may be helpful first to provide some background about motor representation.

A \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.  
%Imagine someone who, while remaining seated, moves an object from her right to her left, passing it between her hands as she does so. 
%The transition between hands is not something she needs to think or reason about. 
%But if the transition occurs without any pause---if she does not have to wait before releasing the object from her right hand into her left in order to check that the object is securely in her left hand---this is a sign that her action involves predicting the position of her left hand.
%***continue this example?
We follow several psychologists and philosophers in supposing that motor representations feature in planning and monitoring action \citep[e.g.][]{wolpert:1995internal, miall:1996_forward}.
[*HY asks why focus here on forward models]

Motor representations are in some ways similar to intentions,
as some have recently argued (\citealp[pp.\ 189-90]{pacherie:2008_action}; \citealp{butterfill:2012_intention}).
First, like intentions, some motor representations represent outcomes and not merely kinematic features of action.
Like intentions, some motor representations play a role in coordinating multiple  component activities by virtue of their role as elements in hierarchically structured plans.
And, like intentions, some motor representations coordinate these activities in a way that would normally facilitate the outcome’s occurrence.

One major dissimilarity between intentions and motor representations is that motor representations lead a kind of double life.
For motor representations are involved not only in producing actions but also in observing actions. Indeed there seem to be some striking similarities between the sorts of processes and representations usually involved in performing a particular action and those which typically occur when observing someone else perform that action \citep{rizzolatti_functional_2010,rizzolatti_mirrors_2008}.%
\footnote{ 
If motor representations occur in action observation, then observing actions might sometimes facilitate performing compatible actions and interfere with performing incompatible actions.  Both effects do indeed occur, as several studies have shown \citep{brass:2000_compatibility, craighero:2002_hand, kilner:2003_interference, costantini:2012_does}. 
}

[*HY: I'm still thinking about how best to introduce motor representation: any pointers?]

So much for the bare notion of motor representation.
Why suppose that motor representation might be needed to explain shared agency?

@@

\section{Social motor representation}
We start from an empirical premise which is about enabling conditions for shared agency only: some joint actions are facilitated by reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent.

This needs unpacking. 
As already mentioned, a \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.
To repeat, motor representations are not concerned with merely kinematic or dynamic features of actions only.
Rather, some motor representations represent outcomes, such as the movement of a target object from one place to another.

A representation (motor or not) is \emph{agent-neutral} if its content does not specify any particular agent or agents.%
\footnote{
Our use of the term `agent-netural' to describe motor representations bears no relation to the use of the same term  to describe reasons \citep[on the latter, see][]{Parfit:1984fk}.
}
To illustrate, agent neutral representations are sometimes found at the early stages of planning.
Imagine that you and some friends are tasked with preparing a holiday.  
You might first write down a plan of action without specifying who will act; the plan simply describes what is to be done.
The plan  will eventually be implemented by you and your friends
 but this is not written in plan itself  and so it is agent-neutral.
Of course the fact that this plan is your collective plan may be represented elsewhere; this fact may also be implicit in  the plan's being stapled to the door of your communal kitchen.
The agent-neutrality of a representation does not require that the agents are nowhere specified, only that they are not specified in the content of the representation.%
\footnote{
Strictly the following argument does not hinge on the agent-neutrality of representations.
It is sufficient for our purposes that there are reciprocal motor representations  of outcomes whose obtaining would normally involve action on the part of each of the reciprocating agents.
In principle such representations could have contents which specify other agents or multiple agents. 
We focus on agent-neutral representations to show that our view is consistent with the possibility that reciprocal motor representations are agent-neutral. 
}

Two or more agents have \emph{reciprocal} motor representations  just if there is a single outcome and each agent has a motor representation of that outcome. 
It is hardly controversial that reciprocal motor representations exist, for their existence is suggested by by a large body of research on motor cognition in action observation.
[***Rest of this paragraph belongs in the evidence section?
Should be clearer about transition:
(a) I am observing and we reciprocally represent an outcome of your action (mirroring).
(b) We are interacting and reciprocally represent an outcome of your action (mirroring in joint action).
(c) We are interacting and reciprocally represent an outcome to which our actions are distributively directed.%
] 
It is more controversial that reciprocal motor representation occurs in joint action, but there is some evidence for this claim too.%
\footnote{
See \citet{kourtis:2012_predictive}: `the partner’s expected action is simulated at the motor level, which probably facilitates effective performance of the joint action.'
\citet{kourtis:2010_favoritism} show that 
reciprocal motor representation is more likely to occur in joint action than is mere observation. 
See also \citet{Knoblich:2003nf}.
 }

We want to go a tiny step further and suggest that in joint action there are sometimes reciprocal, agent-neutral representations of outcomes whose obtaining would normally involve action on the part of each of the agents.
So when we act together, some of my motor representations may concern outcomes that are partly but not entirely to be realised by my actions (and likewise for you).
For example, suppose our task is to move an object from A to B, where you pick it up and pass it to me so that I can then place it.
In this case I may represent the movement of the object from A to B and not only the component movements.
I represent a collective outcome of our actions and not just outcomes to which each of our actions are individually directed.
%
%So it is not just that, when we act together, I represent the outcomes to which your actions are directed and the outcomes to which my actions are directed; I may also represent an outcome to which all of our actions are directed.

We shall use the term \emph{social} motor representation as an abbreviation for the reciprocal, agent-neutral motor representation of outcomes whose obtaining would normally require action on the part of each reciprocating agent.
(This is probably a bad term to pick; we are still trying to come up with a better one. 
Certainly we cannot assume in advance of argument that such reciprocal, agent-neutral motor representations are social in any interesting sense;
for now we are using the term `social' in a non-standard way as an abbreviation, one that reflects our aim.)

What follows is speculative philosophy: we take for granted that  social motor representation sometimes facilitates joint action and ask whether this conjecture bears on our question about shared agency.
As a first step, we shall ask how social motor representation might facilitate joint action.
Note that answering this question does not directly commit us to any view about shared agency.
After all, social motor representation might be an enabling condition for some instances of shared agency but completely unnecessary for explaining what shared agency is.

@@

Suppose that Aravinda runs the trains and Gerhard  the busses.
Let us stipulate that we measure the extent to which the two services, train and bus, are coordinated is to be measured by the sum of all passengers' total journey times.
So new timetables would result in better coordination than the current timetables just if the new timetables would decrease the sum of passengers' total journey times.
To illustrate, improving coordination might involve having trains arrive at a station shortly before, rather than shortly after, busses depart from there.
Now Aravinda and Gerhard each intend they, Aravinda and Gerhard, coordinate the trains with the busses  to the greatest extent possible given other constraints; and they intend to do this by way of these intentions and meshing subplans of them, and this is common knowledge between them. 
Aravinda and Gerhard thus meet Bratman's sufficient conditions for them to have a shared intention.
Acting on this intention, 
every January Aravinda updates the train timetables and sends Gerhard the changes.
Likewise, Gerhard  updates the bus timetables every June and sends Aravinda the changes.
In this way  each is responsive to the other's intentions and subplans of these. 
Indeed, each may even try to predict changes in the other's subplans and modify their own accordingly.  
But from each individual's point of view, the other's plans are  merely a constraint.

>>>>

\section{***Discussion with Cordula Vesper}
\begin{enumerate}
\item Say more about what shared agency at the start: use the contrast cases instead of examples, and say that it involves some kind of fusing of agency.
\item Note that in the jumping experiments, only the subject with the shorter jump changes what she does depending on the difference in jump-length between the two subjects.  Vesper et al interpret this as showing that the subject with the shorter jump plans the whole activity.  But it isn't obviously reciprocal: there is no evidence that the subject with the longer jump is similarly planning.  And this makes sense: here they achieve coordination by first distributing roles (a strategy) and then having at least one subject plan both actions (so there is slightly less reliance on the two plans coinciding).  
Of course the appearance that they are distributing roles might just be an artefact of reciprocal planning where the upshot of the planning is that the person with the longer jump just does what she would normally do.

\item {[done]}  Don't say `neither shared nor an intention' unless you explain this.
\item {[done]} Can cite \citet{konvalinka:2010_follow} as example of what happens when two people each try to predict the other.
\end{enumerate}

@@

\section{Introduction}
When members of a flash mob in the Central Cafe respond to a pre-arranged cue by noisily opening their newspapers, they exercise shared agency. 
But when someone not part of the mob just happens to noisily open her newspaper in response to the same cue, her action does not involve shared agency.%
\footnote{
See \citet{Searle:1990em}; in his example park visitors simultaneously run to a shelter, in once case as part of dancing together and in another case because of a storm. 
Compare \citet{Pears:1971fk} who uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
}
To give another example, 
 two former members of the mob exercise shared agency when they 
   later walk to the metro station together. 
But two people who merely happened to be walking to the metro station side by side would not be exercising shared agency \citep{gilbert_walking_1990}. 
These sorts of case invite the question, 
How do actions involving shared agency differ from merely parallel actions involving  only individual agency?

The first example shows that the difference between shared agency and parallel individual agency can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too. 
And the second example shows that the difference can’t just be a matter of coordination, because people who are merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Apparently, then, systematically distinguishing cases of shared agency from cases of parallel but merely individual agency  requires reflection on causes of actions.

%
%Shared agency is paradigmatically involved when two (or more) people 
%	paint a house together \citep{Bratman:1992mi}, 
%	lift a heavy sofa together \citep{Velleman:1997oo}, 
%	prepare a hollandaise sauce together \citep{Searle:1990em}, 
%	go to Chicago together \citep{Kutz:2000si}, 
%	and walk together \citep{gilbert_walking_1990}.
%In developmental psychology paradigm cases involving shared agency include  two people 
%	tidying up the toys together \citep{Behne:2005qh},
%	cooperatively pulling handles in sequence to make a dog-puppet sing \citep{Brownell:2006gu},
%	bouncing a ball on a large trampoline together \citep{Tomasello:2007gl}.

Which representations %and processes 
are needed to distinguish shared from individual agency?
Philosophers have so far considered intentions and commitments but ignored the possibility that appeal to motor representations may also be needed. 
%To considerations jointly motivate considering whether fully characterising shared agency may require appeal to motor representation.
By contrast, concerning individual rather than shared agency, some have argued that motor representation may play a role in explaining agency \citep[e.g.][]{pacherie:2000_content,pacherie:2008_action,butterfill:2012_intention}. 
In addition, scientific research provides evidence that motor representations sometimes play a role in enabling agents to exercise shared agency, as we shall explain in detail below.
So it is possible to ask whether appeal to motor representation  %might not only sometimes enable agents to exercise shared agency but also
could also play a role in distinguishing shared from individual agency.
In this paper we argue that it could.
Shared agency is not always only a matter of our intentions or commitments: in some cases it also constitutively involves certain structures of motor representation.
Or so we aim to show.

Before going further,
let us step back to ask 
	why it might be useful 
	to  distinguish systematically between shared and individual agency?
Shared agency raises a tangle of scientific and philosophical questions.  Psychologically we want to know which mechanisms make it possible \citep{Sebanz:2006yq,vesper_minimal_2010}.  
Developmentally we want to know when shared agency emerges, what it presupposes and whether it might somehow facilitate socio-cognitive, pragmatic or symbolic development \citep{Moll:2007gu,Hughes:2004zj,Brownell:2006gu}.  
Phenomenologically we want to characterise what (if anything) is special about experiences of action and agency when shared agency is involved \citep{Pacherie:2010fk}.  
Metaphysically we want to know what kinds of entities and structures are implied by the existence of shared agency \citep{Gilbert:1992rs,Searle:1994lb}.  
And normatively we want to know what kinds of commitments (if any) are entailed by shared agency and how these commitments arise \citep{Roth:2004ki}.
%, plus a formal account of how practical reasoning for joint action differs (if at all) from individual practical reasoning \citep{Sugden:2000mw,Gold:2007zd}
A philosophical account of shared agency 
that made it possible to systematically distinguish shared from individual agency  
may support investigation of these questions (as \citealp{Bratman:2009lv} suggests).  
%Or, if there is more than one form of shared agency, the account should provide a principled way of distinguishing among forms of individual and shared agency.

As already mentioned, our aim is to show that distinguishing individual from shared agency sometimes involves appeal to certain structures of motor representation.
Our first step is to review standard approaches to shared agency.

\section{Shared intention}
On the leading, best developed accounts of shared agency in philosophy and psychology, 
shared agency is explained  in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared intention.
For two or more agents to exercise shared agency is for them to have a shared intention and for this shared intention to be appropriately related to their actions.
Such actions comprise a \emph{shared intentional activity} (\citealp[p.\ 142]{Bratman:1999fr}).%
%On this widely held view, the difference between our walking together and two strangers merely walking side-by-side is that one event is appropriately related to a shared intention whereas the other is not.

Explaining shared agency in terms of shared intention pushes us back to the question, What is shared intention?
Here is much disagreement.
Some hold that it differs from
ordinary intention with respect to the attitude involved (\citealp{Searle:1990em}). 
Others have explored the notion that it differs from ordinary intention with respect to its subject, which is plural \citep{Gilbert:1992rs,helm_plural_2008}, 
or that it differs from ordinary intention in the way it arises, namely through team reasoning \citep{Gold:2007zd}, 
or that it involves distinctive obligations or commitments to others (\citealp{Gilbert:1992rs}; \citealp{Roth:2004ki}).
Opposing all such views, \citet{Bratman:1992mi,Bratman:2009lv} argues that shared intention can be realised by multiple ordinary individual intentions and other attitudes whose contents interlock in a distinctive way.

To avoid having to take sides on what shared intention is, 
let us abstract the details
and focus on features that everyone should agree on.
Minimally, a shared intention stands to the actions comprising a shared intentional activity in roughly the way that an ordinary, individual intention stands to an ordinary, individual action.
Now an ordinary, individual intention represents an outcome, coordinates an agent's actions, and coordinates the agent's actions in such a way that, normally, this coordination would facilitate the occurrence of the represented outcome.
Similarly, 
on almost any account,
a shared intention involves there being a single outcome which each agent represents, where these representations coordinate the several agents' actions and coordinate them in such a way that, normally, the coordination would facilitate the occurrence of the represented outcome.

There is another feature of shared intention that should be uncontroversial.  
Shared intentions or their components feature in practical reasoning alongside ordinary, individual intentions,
 and there are normative requirements which apply to combinations of individual and shared intentions.
To illustrate, tonight there is a party and a ceremony.
It is impossible for anyone to attend both, and this is common knowledge among us.
We have a shared intention that we attend the ceremony together.
While having this shared intention, I also intend to go to the party. 
Give our common knowledge,
this combination of shared and individual intentions is irrational. 
Its irrationality is related to that which would be involved in my individually intending to attend the ceremony while also intending to go to the party.
In short, shared intentions or their components are inferentially and normatively integrated with ordinary, individual intentions.

So much for shared intention.
Can we give a full account of shared agency by saying (roughly) that exercises of shared agency involve agents acting on a shared intention?
Or are further ingredients necessary in systematically distinguishing shared from individual  agency?
Our view is that further ingredients are necessary.
In giving a full account of shared agency, it is also necessary to appeal to certain structures of motor representation. 
Note, however, that our view is consistent with various weaker claims linking shared intention to shared agency.
Our view is consistent with the claim that appeal shared intention is also needed in giving an account of shared agency,  
%and with the claim that \emph{some forms} of shared agency can be fully characterised by appeal to shared intention alone.
and with the claim that all exercises of shared agency involve shared intentions in some way.%
\footnote{
On the latter claim, see \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  
Related claims are made by 
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si},  
	\citet[p.\ 117]{rakoczy_pretend_2006},  and
	\citet{Tollefsen:2005vh}.
}

\section{An objection}
At this point opponents sometimes attempt to dismiss our view out of hand along these lines.
Philosophers are interested in shared \emph{intentional} agency. 
If there are forms of shared agency other than this one, we might be right to claim that understanding these will require appeal to motor representation.
But---so the objection---such forms of shared agency (if they exist at all) are not of interest to philosophers. 
So we are clearly wrong to claim that the philosophical project of distinguishing shared from individual agency might require appeal to ingredients other than shared intentions.

One possible response to this line of opposition would be to weaken our claim. 
We could become neutral on whether a full account of the sort of shared agency philosophers have focussed on can be given without appeal to motor representation,
but insist that there is a form of shared agency about which parallel philosophical questions arise. 
This conciliatory response would preserve most of the key claims in what follows, but a stronger response is available.

As mentioned above, some have argued that fully characterising individual agency requires appeal to motor representation as well as intention \citep{pacherie:2000_content,butterfill:2012_intention}. 
These arguments concern intentional action.
So if (as we suppose) these arguments are not known to be defective,
then, assuming a parallel between individual and shared agency,  
it should not be assumed at the outset that appealing to motor representation in a philosophical account of shared agency implies that the account does not apply to what opponents call `shared intentional agency'.
We do not state our position in exactly the terms used by our opponent because of doubts about the qualifier `intentional' that are not specific to discussions of shared agency.\footnotemark \  \ 
However, we do aim show in what follows that a philosophical account of the sort of shared agency that philosophers have been interested in will require appeal to structures of motor representation.

\footnotetext{ 
We avoid using the qualifier `intentional' for reasons not specific to questions about shared agency. 
(We do use the term `shared intentional activity', but our use merely follows Bratman's stipulation that this term applies to an activity appropriately related to a shared intention.)
Briefly, some philosophers offer reasons for holding that there could be agents whose actions are intentional although  the agents have no intentions at all.
For instance, Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' (\citeyear[p.\ 251]{bratman:2000_valuing}; see \citealp[pp.\ 137--8]{Bratman:1987xw} for further justification). 
These and related considerations reveal a coherent and natural way of using the term `intentional' on which it would apply to actions in virtue of their being appropriately related to motor representations of outcomes to which they are directed. 
It is not obvious to us whether using the term in this way is incorrect.
}

\section{Shared motor representation}
Our argument starts with an empirical premise about enabling conditions for shared agency: there are reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent;
moreover, these structures of motor representation sometimes facilitate coordination when agents exercise shared agency.
This needs unpacking. 
So before considering evidence for this premise (in the next section), let us first explain  it.

A \textit{motor} representation is the sort of representation that enables agents to reach for, grasp and transfer objects in a coordinated and fluid way. 
Motor representations play a key role in monitoring and planning actions  \citep[e.g.][]{wolpert:1995internal, miall:1996_forward,Wilson:2005qu}.
Unlike intentions and related mental states, motor representations are usually involved in planning actions over milliseconds rather than minutes or even years.

Some motor representations resemble intentions  in 
	representing outcomes (rather than merely kinematic or dynamic features of action), 
	coordinating multiple  component activities by virtue of their role as elements in hierarchically structured plans,
	and coordinating these activities in a way that would normally facilitate the represented outcome's occurrence (\citealp{hamilton_action_2008}; \citealp[pp.\ 189-90]{pacherie:2008_action}; \citealp{butterfill:2012_intention}).
Despite these points of similarity, 
motor representations can be distinguished from intentions and other action-related intentions,
	 as well as from perceptual representations,
	 by their representational format \citep{butterfill:2012_intention}.

Motor representations lead a kind of double life.
For motor representations are involved not only in producing actions but also in observing actions. 
Indeed there are some striking similarities between the sorts of processes and representations usually involved in performing a particular action and those which typically occur when observing someone else perform that action.
In some cases it is almost as if the observer were planning the observed action, only to stop just short of performing it herself.%
\footnote{ 
For reviews, see \citet{jeannerod_motor_2006,rizzolatti_mirrors_2008,rizzolatti_functional_2010}.
If motor representations occur in action observation, then observing actions might sometimes facilitate performing compatible actions and interfere with performing incompatible actions.  Both effects do indeed occur, as several studies have shown \citep{brass:2000_compatibility, craighero:2002_hand, kilner:2003_interference, costantini:2012_does}. 
}
When motor representations of outcomes trigger a planning-like process in action observation, this may allow the observer to predict others' actions \citep{Flanagan:2003lm,ambrosini:2011_grasping,ambrosini:2012_tie,Costantini:2012fk}.

A representation (motor or not) is \emph{agent-neutral} if its content does not specify any particular agent or agents.%
\footnote{
Our use of the term `agent-netural' to describe motor representations bears no relation to the use of the same term  to describe reasons \citep[on the latter, see][]{Parfit:1984fk}.
}
To illustrate, agent neutral representations are sometimes found at the early stages of planning.
Imagine that you and some friends are tasked with preparing a holiday.  
You might first write down a plan of action without specifying who will act; the plan simply describes what is to be done.
The plan  will eventually be implemented by you and your friends
 but this is not written in plan itself  and so it is agent-neutral.
Of course the fact that this plan is your collective plan may be represented elsewhere; this fact may also be implicit in  the plan's being stapled to the door of your communal kitchen.
The agent-neutrality of a representation does not require that the agents are nowhere specified, only that they are not specified in the content of the representation.%
\footnote{
Strictly the following argument does not hinge on the agent-neutrality of representations.
It is sufficient for our purposes that there are reciprocal motor representations  of outcomes whose obtaining would normally involve action on the part of each of the reciprocating agents.
In principle such representations could have contents which specify particular agents. 
However, we focus on agent-neutral representations to show that our view is consistent with the possibility that reciprocal motor representations are agent-neutral. 
}

Two or more agents have \emph{reciprocal} representations (motor or not) just if there is a single outcome and each agent has a motor representation of that outcome. 
Reciprocal representations can occur both when one agent observes another acting alone and also when two or more agents act together.
Where one agent observes another acting alone,
it is possible that both have motor representations of an outcome to which the agent's action is directed.
For the agent, this representation plays a role in planning and monitoring; for the observer, this representation may facilitate prediction and recognition.
This is one case of reciprocal motor representation---or, as it is more usually called, mirroring.
But our main interest is in a different case,
one where two or more agents are acting together,
 there is a single outcome to which their actions are directed,
 and the agents each have a motor representation of this outcome.
In this case of reciprocal motor representation, the agents each represent an outcome whose obtaining would normally involve not only their own actions but also those of other agents.%
\footnote{ 
	Note that our having reciprocal motor representations would not by itself imply that we know that the represented outcome's obtaining would normally involve actions other than our own.
}
So when we act together, some of my motor representations may concern outcomes that are partly but not entirely to be realised by my actions; and likewise for you.
To illustrate, suppose our task is to move an object from A to B, where you pick it up and pass it to me so that I can then place it.
In this case I may represent the movement of the object from A to B and not only the component movements.
I represent a collective outcome of our actions and not just outcomes to which each of our actions are individually directed.
%
%So it is not just that, when we act together, I represent the outcomes to which your actions are directed and the outcomes to which my actions are directed; I may also represent an outcome to which all of our actions are directed.

We shall use the term \emph{shared} motor representation as an abbreviation for the reciprocal, agent-neutral motor representation of outcomes whose obtaining would normally require action on the part of each reciprocating agent. 
Note that shared motor representations are shared only in the sense in which two people can share a name.  
(We do not mean to suggest that they are shared in the sense in which two people can share a parent: there need be no representation with two or more subjects.)
Note also that a shared motor representation is not a special kind of motor representation: it is merely a structure of ordinary motor representations. 
At this stage we are not strictly entitled use the term `shared motor representation' as an abbreviation.
After all, we have yet to show that these structures of motor representation play a constitutive role in explaining shared agency, or even an enabling role; 
we have yet to review evidence that they exist.
So the choice of term merely reflects our aim.

@@

It is hardly controversial that reciprocal motor representations exist, for their existence is suggested by by a large body of research on motor cognition in action observation.
[***Rest of this paragraph belongs in the evidence section?
Should be clearer about transition:
(a) I am observing and we reciprocally represent an outcome of your action (mirroring).
(b) We are interacting and reciprocally represent an outcome of your action (mirroring in joint action).
(c) We are interacting and reciprocally represent an outcome to which our actions are distributively directed.%
] 
It is more controversial that reciprocal motor representation occurs in joint action, but there is some evidence for this claim too.%
\footnote{
See \citet{kourtis:2012_predictive}: `the partner’s expected action is simulated at the motor level, which probably facilitates effective performance of the joint action.'
\citet{kourtis:2010_favoritism} show that 
reciprocal motor representation is more likely to occur in joint action than is mere observation. 
See also \citet{Knoblich:2003nf}.
 }

What follows is speculative philosophy: we now take for granted that  social motor representation sometimes facilitates the exercise of shared agency and ask whether this matters for a philosophical account of shared agency. 
As a first step, we shall ask how social motor representation might facilitate agents in coordinating their actions.
Note that answering this question does not directly commit us to any view about shared agency.
After all, social motor representation might sometimes facilitate coordination while being extraneous to a philosophical account of shared agency.

@@

In small city state, Aravinda organises the trams and Gerhard the busses.
Each is responsible for devising and updating the timetable for the service.
Let us stipulate that the extent to which the tram and bus services are coordinated is to be measured by the sum of all passengers' total journey times.
So a change to the timetables would result in better coordination  just if it would decrease the sum of passengers' total journey times.
To illustrate, improving coordination might involve having trams arrive at a stop shortly before, rather than shortly after, busses depart from there.
Now Aravinda and Gerhard each intend they, Aravinda and Gerhard, coordinate the trams with the busses  to the greatest extent possible given other constraints; and they intend to do this by way of these intentions and meshing subplans of them, and this is common knowledge between them. 
Aravinda and Gerhard thus meet Bratman's sufficient conditions for them to have a shared intention.
Acting on this intention, 
every January Aravinda updates the tram timetables and sends Gerhard the changes.
Likewise, Gerhard  updates the bus timetables every June and sends Aravinda the changes.
In this way  each is responsive to the other's intentions and subplans of these. 
Indeed, each may even try to predict changes in the other's subplans and modify their own accordingly.  
But from each individual's point of view, the other's plans are  merely a constraint.
